
% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Seth M.}{Calkins}           % Your name
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{skills}
%  \vspace{-0.2cm}
%
%Skill 1, skill 2, skill 3, skill 4, skill 5.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {01/2015 - Now~~~~~}
  {Liquid Communications}
  {Noblesville, IN}
  {\jobtitle{IT Business Analyst}\\
  Identify new technologies, products, and equipment to support business operations, managing procurement processes, and ensuring seamless introduction of new technology and equipment into existing infrastructure.\\
\begin{itemize}
\item Develop proper planning of corporate infrastructure by prioritizing IT investments, performing risk mitigation, managing internal software development and application deployment, and providing technical project oversight.
\item Facilitate the design and implementation of new/improved process models to ensure milestones are met and results are achieved.
\item Exceptional analysis and recommendation capability; Proactively identify trends and opportunities to increase profitability, stay ahead of business, and keep the team informed, focusing on future profitability impacts.
\item Develop and incorporate pricing, sales and sales channel creation, service development, cost reduction, and technology strategies.
\item Strategically managed all aspects of company infrastructure, application, support, and security. Shaped and managed implementation of company IT strategy. Educated staff on proper use of technology through delivery of engaging and effective change management programs.
\item Provide relevant support to the senior management in order to identify strategic goals, objectives, scope, budgets, and processes for project development.
\item Utilize effective problem solving skills in developing solution documentation, analyzing solutions, and validating IT to meet business goals and objectives as well as effectively manage change requests.

\end{itemize}
}
%------------------------------------------------
\entry
  {March 2014--May 2015~~~~~~~} 
  {Creative Solutions Consulting}
  {Indianapolis, Indiana}
  {\jobtitle{System Analyst}\\
 Keen ability to leverage technology to achieve strategic goals\\
  \begin{itemize}
\item Develop viable IT solutions to reduce operational expenses and boost company's competitive edge.
\item Oversaw the effective provisioning, installation/configuration, operation, and maintenance of systems hardware and software and related infrastructure in compliance with DoD security policies.
\item Responsible for installing, configuring, monitoring, maintaining, and troubleshooting hardware and software applications, including servers, desktops, laptops, and, smart phones.
\item Initiated, planned, and supervised the design and configuration of DARPA contractors' workstations VPN site-to-site, and User VPN access, created access rules to block ports, applied web filters to users or groups, switching ISP's or static IP addresses.
\item Assisted with recruitment advertising, incorporating employment brand while recommending new sites/tools to drive timely and cost-efficient hiring with the best talent on the market.
\item Collaborated with members of the recruiting team to develop and lead recruiting efforts, effectively generate qualified leads targeted in tough-to-fill Information technology markets.
\item Ensured maintenance of network infrastructure including Internet connections, perimeter equipment, Network switches, Wireless access.
\item Orchestrated the ongoing support of the Windows server hosting infrastructure.
\item Oversaw the Active Directory and Exchange servers, including system administrator engineering and provisioning, operations and support, maintenance, and research and development to ensure continual innovation.
\item Conducted research on targeted companies and passive candidates, leveraging undocumented API's.
\item Ensured continuous research on recruitment marketing tools and resources to make first class recommendations available to the team.
  \end{itemize}}
%------------------------------------------------
% * <seth.calkins88@gmail.com> 2016-08-18T20:11:07.436Z:
%
% over printing... how to do new page?
%
% ^.
\entry
  {Oct. 2011--March 2014}
  {Indycom}
  {Noblesville, IN}
  {\jobtitle{Business Development, Strategy \& Planning}\\
Developed and lead the Business Development team in sourcing, managing, and implementing new business opportunities.\\

\begin{itemize}
\item Planned, designed and implemented, physical and logical network infrastructure based on business analysis, including, LAN Server, website deployment/design, email, desktop/mobile device management/deployment, VOIP phone system.,
\item Perform analysis and propose ways to enhance the companies digital media image (websites, social media, directory listings) on an ongoing basis, to reach more clientele by tapping into areas not formerly utilized.
\item Designed a highly effective customer database system to track leads, customers, emails, phone calls, meetings, reminders, and opportunities.
\item Designed and developed procedures for timely and appropriate record keeping, billing, data management, invoices, and information system reports.
\item Developed Social Media strategies and policies; Implemented, maintained, and analyzed marketing campaigns.
\item Exceptional analysis and recommendation capability; Proactively identify trends and opportunities to increase profitability, stay ahead of business, and keep the team informed, focusing on future profitability impacts.
\item Develop and incorporate pricing, sales and sales channel creation, service development, cost reduction, and technology strategies.
\end{itemize}}

\end{entrylist}
%------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\patchcmd\entry
{May 2014 - March 2016}
{M.Sc. {\normalfont in Economics [Grade]}}
{University}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2004--2009}
{B.Eng. {\normalfont in Engineering Management [Grade]}}
{University}
{(Emphasis in ...)}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{other qualifications}

\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{Qualification}
{Institution}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2011}
{Qualification}
{Institution}
{\vspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{Award name}
{Institution}
{Award description. Award description. Award description. Award description. Award description. Award description. Award description. }
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}
  \vspace{-0.2cm}

\textbf{professional:} professional interest 1, professional interest 2 and professional interest 3. \textbf{personal:} personal interest 1, personal interest 2, personal interest 3 and personal interest 4.

%----------------------------------------------------------------------------------------

\end{document}